Supplementary Material for `The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere'

### 2023-11-28 manuscript.tex
Update manuscript.tex

@@

\subsubsection{4.1 Main stressors effects on food webs in a southwest
Atlantic - Antarctic
gradient}\label{main-stressors-effects-on-food-webs-in-a-southwest-atlantic---antarctic-gradient}

>>>>

\subsection{Running Title: Marine stressors in the Southern
Hemisphere}\label{running-title-marine-stressors-in-the-southern-hemisphere}

@@

\subsubsection{4.1 Main stressor effects in food webs in a southwest
Atlantic - Antarctic
gradient}\label{main-stressor-effects-in-food-webs-in-a-southwest-atlantic---antarctic-gradient}
